\documentclass{beamer}

\usetheme{Warsaw}
\title{GFX Team Retrospective Meeting}

\begin{document}
\maketitle

\begin{frame}
\frametitle{Attack plan}
\begin{enumerate}
    \item Warm up [last sprint results]
    \item \textbf{The moment of truth [last year retrospective]}
    \item \textbf{Fight strategy [creating action plan]}
    \item Post-match comments [reflection on meeting]
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Last sprint results}
\centering{{\Large \textbf{Quick look into statistics :)} \par}}
\end{frame}

\begin{frame}
\frametitle{Last sprint results}
\centering{{\Large \textbf{Quick look into statistics :)} \par}}
\bigbreak
\centering{{\Huge \textbf{We've met our goal!} \par}}
\centering{{\Huge \textbf{Congratulations!} \par}}
\end{frame}

\begin{frame}
\frametitle{Last sprint results}

\begin{block}{Dear Customer...}
...as a team we are proud of the work we did in this sprint because...
\end{block}

\begin{block}{Dear Manager...}
...we are proud of how we engaged as a collaborative team in this sprint because...
\end{block}

\begin{block}{Dear Team...}
...I am proud of how I contributed in this sprint because...
\end{block}

\end{frame}

\begin{frame}
\frametitle{Main course}
\centering{{\Huge \textbf{Time has come...} \par}}
\end{frame}

\begin{frame}
\frametitle{Big picture}

\begin{block}{Results}
    \begin{itemize}
        \item What specific work have we accomplished?
        \item What problems have we been able to solve?
      \end{itemize}
\end{block}

\begin{block}{Improvement and deterioration}
    \begin{itemize}
        \item How have we changed the way we work since last year?
      \end{itemize}
\end{block}

\begin{block}{Side view}
    \begin{itemize}
        \item What are people saying about our team and how it works?
        \item What do we tell others about our team?
      \end{itemize}
\end{block}

\end{frame}

\begin{frame}
\frametitle{Team Vision}

\begin{itemize}
    \item What worked well that we \textbf{don't want to forget}?
    \item What we \textbf{learned}?
    \item What we should \textbf{do differently next time}?
    \item What still \textbf{puzzles us}?
    \item What may \textbf{still be missing}?
    \item What we see that \textbf{worries us}?
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Team Vision}

\begin{itemize}
    \item What worked well that we \textbf{don't want to forget}?
    \item What we \textbf{learned}?
    \item What we should \textbf{do differently next time}?
    \item What still \textbf{puzzles us}?
    \item What may \textbf{still be missing}?
    \item What we see that \textbf{worries us}?
\end{itemize}
\bigbreak
\centering{{\Huge \textbf{Let's create Action Plan!} \par}}
\end{frame}

\begin{frame}
\frametitle{Reflect on the meeting}

\begin{itemize}
    \item Do you feel we should address anything else?
    \item Do we need to discuss something in greater detail?
    \item \textbf{Have you met your personal objectives for attending this meeting ?}
\end{itemize}
\end{frame}

\begin{frame}

\begin{frame}
\frametitle{Struggles}

\begin{itemize}
    \item I know we are all engeneers and so we have problems with jumping straight to solutions. 
    \item Team has tendency (and really like it) to drift away from the main subject of the meeting. Especially when we can start some kind of tech-talk :)
    \item The bolded fragments are hints for me - what I what to emphasise or what I want to write on white board during the meeting.
    \item It was much longer, but I feel that we gathered more insight then usually - even related to the last or 2 previous sprints.
\end{itemize}
\end{frame}

\begin{frame}

\frametitle{Time for lunch}

\centering{{\Huge \textbf{Thank you!} \par}}
\end{frame}

\end{document}